---
title       : Life Satisfaction
subtitle    : Preliminary Results
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
hitheme: solarized_light
assets:
  css:
  - "http://fonts.googleapis.com/css?family=Raleway:300"
  - "http://fonts.googleapis.com/css?family=Oxygen"
--- 
<style>
iframe{
  height:450px;
  width:900px;
  margin:auto auto;
}

body{
  font-family: 'Raleway', sans-serif;
}


h1,h2,h3,h4 {
  font-family: 'Raleway', sans-serif;
}

</style>

```{r set.global.options, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(comment = NA, echo=F, results = 'asis', tidy = F, message = F)
```


```{r external.code}
chunk.dir <- 'G:\\research\\mrp\\brfss\\Life_Sat_Results1\\chunks\\'
read_chunk(paste(chunk.dir,"chunks_A.R",sep=""))
```

```{r load.libraries.pres}
```

```{r functions.for.presentation}
```

```{r load.mcmc.runs}
```

```{r load.data}
```

### Data 

- Behavioral Risk Factor Surveillance System, 2005-2010.
- Total Sample Size: `r prettyNum(dim(tmp.dat)[1], big.mark=",", scientific=F)` respondents
- Dependent Measure: Life Satisfaction = "In general, how satisfied are you with your life?"


--- &twocol w1:40% w2:55%

### Data   
    
*** {name: left}
    
- Behavioral Risk Factor Surveillance System, 2005-2010.
- Total Sample Size: <br/>
    `r prettyNum(dim(tmp.dat)[1], big.mark=",", scientific=F)` respondents
- Dependent Measure: <br/>
    Life Satisfaction = "In general, how satisfied are you with your life?"
    
*** {name: right}


```{r plot.histogram.satisfaction,fig.keep='none', cache=F, fig.align='right'}
```

--- &basic1

### Model

- Logit with 
  - 1="Very Satisified"
  - 0="Satisfied", "Dissatisfied","Very Dissatisfied"
- Independent Measures: X=(Income, Number of Children, Marital Status, Race, Gender, Age, Gender*Age)
- All measures are interacted with respondent's state of residence in a multi-level model:
$$
{\rm Pr}(S_{i}=1) = \frac{ \exp\{X_i'\beta_{s_i}\} }{ 1 + \exp\{X'\beta_{s_i}\}}
$$
where $s_i$ is respondent $i$'s state of residence.

$$
\beta_{s} \sim {\rm N}(\beta,\Sigma)
$$


---

### Predicted Life Satisfaction by (Age,Gender,State)

```{r plot.age.gender.levels, fig.keep='none', cache=F, fig.align='center'}
```


---

### Income and Children Effects by State

```{r plot.income.children, fig.keep='none', cache=F, fig.align='center'}
```

---

### Income and Children Effects by State

```{r plot.married, fig.keep='none', cache=F, fig.align='center'}
```

